### 2012-02-29 Krantz-v3/Chapters/chapter1/experiments.tex
Added figures and captions to the book chapter and added tables of word lists

A specific example of this involves labeling of hospital discharge summaries.  These summaries are authored by clinicians to summarize patient
hospitalization courses. They typically contain a record of patient
complaints, findings and diagnoses, along with treatment and hospital course.  The kind of text one might expect to find in such a discharge summary is illustrated by this made-up snippet
\begin{quote}
{History of Present Illness: Mrs. Carmen Sandiego is a 62-year-old female with a past medical history significant for diabetes, hypertension, hyperlipidemia, afib, status post MI in 5/2010 and cholecystectomy in 3/2009.  The patient presented to the ED on 7/11/2011 with a right sided partial facial hemiparesis along with mild left arm weakness.  The patient was admitted to the Neurology service and underwent a workup for stroke given her history of MI and many cardiovascular risk factors ...}
\end{quote} 
For each hospitalization, trained medical coders review the information in the
discharge summary and assign a series of diagnoses codes. Coding follows the
ICD-9-CM controlled terminology, an international diagnostic classification for
epidemiological, health management, and clinical
purposes.\footnote{http://www.cdc.gov/nchs/icd/icd9cm.htm}  These ICD-9 codes are organized in a rooted-tree structure, with each
edge representing an is-a relationship between parent and child, such that the
parent diagnosis subsumes the child diagnosis. For example, the code for
{}``Pneumonia due to adenovirus'' is a child of the code for {}``Viral
pneumonia,'' where the former is a type of the latter.  A representative sub-tree of the ICD-9 code tree is shown in Figure ADLER\ref{ADLER}. It is worth noting that
the coding can be noisy. Human coders sometimes disagree~\cite{Challenge07},
tend to be more specific than sensitive in their
assignments~\cite{Birmetal2005}, and sometimes make
mistakes~\cite{FarzandipourEtAl10}.

@@

Amazon.com is one such retailer.  Their product categorization data is available as part of the 
 Stanford Network Analysis Platform (SNAP) dataset~\cite{SNAP}.    A representative sub-tree of the amazon.com DVD produce categorization tree is shown in Figure ADLER\ref{ADLER}.  
Product descriptions were obtained separately from the
Amazon.com website directly. Once such description is
\begin{quote}
{Winner of five Academy Awards, including Best Picture and Best Director, The Deer Hunter 
is simultaneously an audacious directorial conceit and one of the greatest films ever made 
about friendship and the personal impact of war. Like Apocalypse Now, it's hardly a conventional 
battle film--the soldier's experience was handled with greater authenticity in Platoon--but its 
depiction of war on an intimate scale packs a devastatingly dramatic punch ... }
\end{quote}
We study the collection of DVDs
in the product catalog specifically.
%We were able to deduce the structure of the
%hierarchy for the Amazon.com products because all ancestors in the
%hierarchy were included with each category label. For example, {}``DVD / Genres
%/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
%for the DVD, {}``The Time Machine.''
The resulting dataset contains 15,130 product descriptions for training and 1,000
for testing. The product descriptions consist of
91.89 terms on average (std dev=53.08). Overall, there are 2,691 unique categories.
Products are assigned on average 9.01 categories (std dev=4.91). The vocabulary
consists of the most frequent 30,000 words omitting stopwords.

@@

Example topics (as word lists) learned for the discharge data are given below.  These word lists are computed by ADLER

\begin{extract}
ADLER
\end{extract}

ADLER could you write a sentence about how these are cleaner than the SLDA or LDA topics?

@@

Example topics (as word lists) learned for the amazon.com data are given below.  T

\begin{extract}
ADLER
\end{extract}

>>>>

A specific example of this involves labeling of hospital discharge summaries.  These summaries are authored by clinicians to summarize patient
hospitalization courses. They typically contain a record of patient
complaints, findings and diagnoses, along with treatment and hospital course.  The kind of text one might expect to find in such a discharge summary is illustrated by this made-up snippet
\begin{quote}
{History of Present Illness: Mrs. Carmen Sandiego is a 62-year-old female with a past medical history significant for diabetes, hypertension, hyperlipidemia, afib, status post MI in 5/2010 and cholecystectomy in 3/2009.  The patient presented to the ED on 7/11/2011 with a right sided partial facial hemiparesis along with mild left arm weakness.  The patient was admitted to the Neurology service and underwent a workup for stroke given her history of MI and many cardiovascular risk factors ...}
\end{quote} 
For each hospitalization, trained medical coders review the information in the
discharge summary and assign a series of diagnoses codes. Coding follows the
ICD-9-CM controlled terminology, an international diagnostic classification for
epidemiological, health management, and clinical
purposes.\footnote{http://www.cdc.gov/nchs/icd/icd9cm.htm}  These ICD-9 codes are organized in a rooted-tree structure, with each
edge representing an is-a relationship between parent and child, such that the
parent diagnosis subsumes the child diagnosis. For example, the code for
{}``Pneumonia due to adenovirus'' is a child of the code for {}``Viral
pneumonia,'' where the former is a type of the latter.  A representative sub-tree of the ICD-9 code tree is shown in Figure \ref{fig:diagnosis_tree}. It is worth noting that
the coding can be noisy. Human coders sometimes disagree~\cite{Challenge07},
tend to be more specific than sensitive in their
assignments~\cite{Birmetal2005}, and sometimes make
mistakes~\cite{FarzandipourEtAl10}.

\begin{figure}[t]
%tbp] %  figure placement: here, top, bottom, or page
\centering \includegraphics[scale=0.4]{Chapters/chapter1/figures/hi_quality_ICD9_tree_cropped} \caption{An illustration of a portion of the ICD9 hierarchy.}
\label{fig:diagnosis_tree}
\end{figure}

@@

\begin{figure}[t]
%tbp] %  figure placement: here, top, bottom, or page
\centering \includegraphics[scale=0.4]{Chapters/chapter1/figures/hi_quality_product_tree_cropped} \caption{An illustration of a portion of the Amazon product hierarchy.}
\label{fig:product_tree}
\end{figure}

Amazon.com is one such retailer.  Their product categorization data is available as part of the 
 Stanford Network Analysis Platform (SNAP) dataset~\cite{SNAP}.    A representative sub-tree of the amazon.com DVD produce categorization tree is shown in Figure \ref{fig:product_tree}.  
Product descriptions were obtained separately from the
Amazon.com website directly. Once such description is
\begin{quote}
{Winner of five Academy Awards, including Best Picture and Best Director, The Deer Hunter 
is simultaneously an audacious directorial conceit and one of the greatest films ever made 
about friendship and the personal impact of war. Like Apocalypse Now, it's hardly a conventional 
battle film--the soldier's experience was handled with greater authenticity in Platoon--but its 
depiction of war on an intimate scale packs a devastatingly dramatic punch ... }
\end{quote}
We study the collection of DVDs
in the product catalog specifically.
%We were able to deduce the structure of the
%hierarchy for the Amazon.com products because all ancestors in the
%hierarchy were included with each category label. For example, {}``DVD / Genres
%/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
%for the DVD, {}``The Time Machine.''
The resulting dataset contains 15,130 product descriptions for training and 1,000
for testing. The product descriptions consist of
91.89 terms on average (std dev=53.08). Overall, there are 2,691 unique categories.
Products are assigned on average 9.01 categories (std dev=4.91). The vocabulary
consists of the most frequent 30,000 words omitting stopwords.

@@

Example topics (as word lists) learned for the discharge data are given below.  These word lists are computed by sorting
terms in decreasing order based on their probability under a given topic.

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline
MASS & WOUND \\
\hline
CANCER & FOOT \\
\hline
RIGHT & CELLULITIS \\
\hline
BREAST & ULCER \\
\hline
CHEMOTHERAPY & LEFT \\
\hline
METASTATIC & ERYTHEMA \\
\hline
LEFT & PAIN \\
\hline
LYMPH & SWELLING \\
\hline
TUMOR & SKIN \\
\hline
BIOPSY & RIGHT \\
\hline
CARCINOMA & ABSCESS \\
\hline
LUNG & LEG \\
\hline
CHEMO & OSTEOMYELITIS \\
\hline
ADENOCARCINOMA & TOE \\
\hline
NODE & DRAINAGE \\
\hline
\end{tabular}
\end{extract}

@@

Example topics (as word lists) learned for the amazon.com data are given below.  These word lists were also computed by sorting
terms in decreasing order based on their probability under a given topic.

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline
SERIES & BASEBALL \\
\hline
EPISODES & TEAM \\
\hline
SHOW & GAME \\
\hline
SEASON & PLAYERS \\
\hline
EPISODE & BASKETBALL \\
\hline
FIRST & SPORT \\
\hline
TELEVISION & SPORTS \\
\hline
SET & NEW \\
\hline
TIME & PLAYER \\
\hline
TWO & SEASON \\
\hline
SECOND & LEAGUE \\
\hline
ONE & FOOTBALL \\
\hline
CHARACTERS & STARS \\
\hline
DISC & FANS \\
\hline
GUEST & FIELD \\
\hline
\end{tabular}
\end{extract}
